---
title: "Correlations figure"
author: "Claus Wilke"
output: html_document
---


Data table, where RSA was calculated using Tien's table and WCN is the side-chain WCN that includes contacts of a side-chain with other side-chains and alpha carbons (for Glys, the side-chain is considered to be at the alpha carbon):

```{r,echo=FALSE}
library(dplyr)
library(tidyr)
library(readr)
library(cowplot)

# set up data table

# read wcn components
df1 <- read_csv("data/prof_out_wcn.csv")

# make pdb column into factor, since read_csv doesn't by default
df1$pdb <- factor(df1$pdb)

# calculate side-chain wcn
df1$wcn.cca <- df1$wcn.ci.cj + df1$wcn.ci.aj
glys <- df1$aa.i == "G"
df1[glys,"wcn.cca"] <- df1[glys,"wcn.ai.cj"] + df1[glys,"wcn.ai.aj"]

# calculate additional columns and clean up
df1 <- df1 %>% group_by(pdb) %>%
  mutate(
    K = r4s.jc.ej/mean(r4s.jc.ej) # normalized relative rates from rates calculated by Elisha using the JC model
  ) %>%
  select(pdb, site, residue=aa.i, K, RSA=rsa.tien, WCN=wcn.cca) # cleaned-up and pared-down table

# show table
head(df1)
```

# Model comparison

Table with predicted-empirical correlations:

```{r, echo=TRUE}
corTable <- df1 %>% group_by(pdb) %>%
  summarize( cor.RSA = cor(K, RSA),
             cor.WCN = cor(K, WCN))
head(corTable)
```

Protein-by-protein model comparison
```{r, echo=TRUE}
# pared-down table of select structures
pdblist <- c("1R44", "1LVH", "1AKO", "1OGO")
justTable <- data.frame(pdb=pdblist,
                        vjust=c(.4, 1.1, 1.1, 1),
                        hjust=c(1.2, 1.2, 1.2, 1.2))
corTable2 <- filter(corTable,
                    pdb %in% pdblist) %>% inner_join(justTable, by='pdb')

p1 <- ggplot(corTable, aes(y=cor.RSA, x=-cor.WCN)) + 
  geom_abline() +
  geom_point(col="blue", size=2) + 
  geom_point(data=corTable2, col='black', size=6, shape=1) +
  geom_text(data=corTable2, aes(label=pdb, vjust=vjust, hjust=hjust), col='black') +
  scale_x_continuous(limits = c(0.25, 0.78), breaks = c(.3, .5, .7)) +
  scale_y_continuous(limits = c(0.25, 0.78), breaks = c(.3, .5, .7)) +
  coord_fixed() +
  xlab("Abs. Rate-WCN correlation") +
  ylab("Abs. Rate-RSA correlation")
#p2 <- switch_axis_position(p1, axis='x') 
#p3 <- ggdraw(p2)

save_plot("cor_fig.pdf", p1, base_height = 5)

p1 
#corTable %>% filter(cor.RSA>-cor.WCN, cor.RSA>.5, cor.RSA<.6)
```

Write data files for select structures
```{r, echo=TRUE}
for(x in pdblist)
{
  df_structure <- df1[df1$pdb==x, ]
  write.csv(df_structure, paste("structures/", x, ".csv", sep=''), row.names=FALSE)
  # multiply by 20 and add 10 to get rates comparable to B factors, for "cartoon putty"
  write.table(10+20*rank(df_structure$K)/nrow(df_structure), paste("structures/", x, "-rate.txt", sep=''), row.names=F, col.names=F)
  write.table(rank(df_structure$RSA)/nrow(df_structure), paste("structures/", x, "-RSA.txt", sep=''), row.names=F, col.names=F)
  write.table((rank(df_structure$K)-rank(df_structure$RSA))/(nrow(df_structure)-1), paste("structures/", x, "-rate-RSA.txt", sep=''), row.names=F, col.names=F)
  write.table(rank(-1*df_structure$WCN)/nrow(df_structure), paste("structures/", x, "-WCN.txt", sep=''), row.names=F, col.names=F)
  write.table((rank(df_structure$K)-rank(-1*df_structure$WCN))/(nrow(df_structure)-1), paste("structures/", x, "-rate-WCN.txt", sep=''), row.names=F, col.names=F)
  cat("pdb:", x, "min WCN:", min(df_structure$WCN), "max WCN", max(df_structure$WCN), "\n")
}
```
